---
title: "Alena Affymetrix Analysis 2016"
author: "Anton Enright"
date: \'`r format(Sys.time(), '%d %B, %Y')`\'
output:
 github_document:
    toc: yes
---


```{r setup, results='hide',message=F, warning=F, echo=F}
require(knitr)
opts_knit$set(root.dir = '/Users/aje/anton_r_notebook/alena_mirna_oct_2016/alena_affy_2017')
opts_chunk$set(dev="png", 
               dev.args=list(type="cairo"),
               dpi=300)
```

# Experiment Setup

CEL Files were provided for both WT and HO samples with 3 replicates and a universal control sample. The control sample was excluded.

This is the sample description file used for the analyses below.

**Sample_ID**|**Genotype**|**Sample_Origin**|**Sample_ID_Plateform**|**Data_FileName**|**Array_Name_Ref**|**Platform_Name**|**Hybridation_Date**|**Platform_QC**|**Species**
--------|------------|-----------|--------------|------|------------
1WT |WT |Other|CM40_ARN0013|CM40_ARN0013_s1h1_mGene2.0.CEL|MoGene-2_0-st|Institut Curie (Paris|42814|Good|Mus musculus 
6WT |WT |Other|CM40_ARN0014|CM40_ARN0014_s1h1_mGene2.0.CEL|MoGene-2_0-st|Institut Curie (Paris|42814|Good|Mus musculus 
7WT|WT|Other|CM40_ARN0015|CM40_ARN0015_s1h1_mGene2.0.CEL|MoGene-2_0-st|Institut Curie (Paris|42814|Good|Mus musculus   
8HO |HO |Other|CM40_ARN0016|CM40_ARN0016_s1h1_mGene2.0.CEL|MoGene-2_0-st|Institut Curie (Paris|42814|Good|Mus musculus 
28HO|HO|Other|CM40_ARN0017|CM40_ARN0017_s1h1_mGene2.0.CEL|MoGene-2_0-st|Institut Curie (Paris|42814|Good|Mus musculus 
29HO |HO |Other|CM40_ARN0018|CM40_ARN0018_s1h1_mGene2.0.CEL|MoGene-2_0-st|Institut Curie (Paris|42814|Good|Mus musculus
Mus_Univ_RNA|Mus_Univ_RNA|Other|CM40_ARN0019|CM40_ARN0019_s1h1_mGene2.0.CEL|MoGene-2_0-st|Institut Curie (Paris|42814|Good|Mus musculus 

## Preparation
We first load the R/BioConductor libraries that we need.
```{r, results='hide',message=F, warning=F}
library(oligo)
library(pd.mogene.2.0.st)
library(mogene20sttranscriptcluster.db)
library(gplots)
library(RColorBrewer)
library(pvclust)
library(colorspace)
library(limma)
library(stringr)
library(genefilter)

```

## Experiment Setup

We change directory to the location of the Affy CEL files.
We load the experimental design and create colour schemes for different plots. 
```{r}

hmcol = colorRampPalette(brewer.pal(9, "GnBu"))(100)
spectral <- colorRampPalette(rev(brewer.pal(11, "Spectral")), space="Lab")(100)
spectral2 <- rev(brewer.pal(11, "Spectral"))

setwd("/Users/aje/anton_r_notebook/alena_mirna_oct_2016/alena_affy_2017")

pdata=read.table("pdata.txt",header=TRUE)
pdata

cond_colours = brewer.pal(length(unique(pdata$Genotype))+1,"Set3")[as.factor(pdata$Genotype)]
names(cond_colours)=pdata$Genotype
```


## CEL File Loading

We load CEL files and extract the *core* expression result per transcript and not exon level data.
```{r}
geneCELs = as.character(pdata$Data_FileName)
affyGeneFS <- read.celfiles(geneCELs)
geneCore <- rma(affyGeneFS, target = "core")
expression=exprs(geneCore)
```

## Initial QC

### Boxplots of Gene Expression Sample to Sample
```{r}
boxplot(affyGeneFS,target="core",las=2,cex.axis=0.8,main="Pre Norm",col=cond_colours,names=pdata$Sample_ID)
legend("topright",levels(pdata$Genotype),fill=cond_colours[levels(pdata$Genotype)],cex=0.5)
boxplot(geneCore,las=2,cex.axis=0.8,main="Post Norm",col=cond_colours,names=pdata$Sample_ID)
```

### Heatmap of expression correlations, Sample to Sample
```{r}
heatmap.2(cor(expression),col=hmcol,trace="none",margin=c(10,10),cexRow=0.7,cexCol=0.7,ColSideColors=cond_colours,RowSideColors=cond_colours,labRow=pdata$Sample_ID,labCol=pdata$Sample_ID,main="Sample to Sample Correlation (Normalised)")
```

### Principal Component Analysis
```{r}
pca <- princomp(expression)
plot(pca$loadings, main="PCA Time", col=cond_colours,  pch=19, cex=2)
text(pca$loadings, as.character(pdata$Sample_ID), pos=3, cex=0.4)
```

## Gene Annotation
Use the affymetrix gene annotation data to extract gene symbols, accessions, descriptions and ensembl IDs per probeset.
We also use these data to restrict to only protein_coding transcripts here (optional).
```{r}
probes = rownames(expression)
genesymbols =  unlist(mget(probes,mogene20sttranscriptclusterSYMBOL,ifnotfound=NA))
genedescs   =  unlist(mget(probes,mogene20sttranscriptclusterGENENAME,ifnotfound=NA))
gene_ens    =  unlist(mget(probes,mogene20sttranscriptclusterENSEMBL,ifnotfound=NA))
featureData(geneCore) <- getNetAffx(geneCore, "transcript")

lincrnas=grep("gene_biotype:lincRNA",pData(featureData(geneCore))[, "mrnaassignment"])
protein_coding=grep("gene_biotype:protein_coding",pData(featureData(geneCore))[, "mrnaassignment"])
non_coding=grep("gene_biotype:non_coding",pData(featureData(geneCore))[, "mrnaassignment"])

# Restrict to protein coding ?
#expression=exprs(geneCore)[protein_coding,]

# Or all genes
expression=exprs(geneCore)
```


```{r}

annotation_table=as.data.frame(matrix(,ncol=4))

insertRow <- function(existingDF, newrow, r) {
  existingDF[seq(r+1,nrow(existingDF)+1),] <- existingDF[seq(r,nrow(existingDF)),]
  existingDF[r,] <- newrow
  existingDF
}

for (i in 1:length(probes)){
  name=strsplit(pData(featureData(geneCore))[probes[i], "geneassignment"],"//")[[1]][2]
  refseq=strsplit(pData(featureData(geneCore))[probes[i], "mrnaassignment"],"//")[[1]][1]
  ensembltrans=strsplit(pData(featureData(geneCore))[probes[i], "mrnaassignment"],"//")[[1]][10]
  desc=strsplit(pData(featureData(geneCore))[probes[i], "mrnaassignment"],"//")[[1]][3]
  name=gsub(" ","",name)
  refseq=gsub(" ","",refseq)
  ensembltrans=gsub("/ ","",ensembltrans)
  ensembltrans=gsub(" ","",ensembltrans)
  desc=gsub("^ ","",desc)
  desc=gsub(" $","",desc)
  #annotation_table[probes[i],"name"]=name
  #annotation_table[probes[i],"desc"]=desc
  #annotation_table[probes[i],"ensembltrans"]=ensembltrans
  #annotation_table[probes[i],"refseq"]=refseq
  insertRow(annotation_table,c(name,desc,ensembltrans,refseq),(nrow(annotation_table)+1))
}
```

## Load TargetScan Targets for mir-29
```{r}
targetscan=read.table("TargetScan7.1__miR-29-3p.predicted_targets.txt",row.names=1,sep="\t",header=T)

symbol_lookup=as.data.frame(genesymbols)
colnames(symbol_lookup)=c("affy_gene_name")
symbol_lookup$affy_id=rownames(symbol_lookup)

targetscan_hits=merge(as.matrix(targetscan),symbol_lookup,by.x=0,by.y=1)
targetscan_list = unique(targetscan_hits$affy_id)

scores=targetscan$Aggregate.PCT
scores=gsub("> ","",scores)
scores=gsub("< ","",scores)
scores=as.double(scores)



targetscan_hits_90 = merge(as.matrix(targetscan[scores >= 0.9,]),symbol_lookup,by.x=0,by.y=1)
targetscan_list_90 = unique(targetscan_hits_90$affy_id)

targetscan_hits_80 = merge(as.matrix(targetscan[scores >= 0.8,]),symbol_lookup,by.x=0,by.y=1)
targetscan_list_80 = unique(targetscan_hits_80$affy_id)

targetscan_hits_70 = merge(as.matrix(targetscan[scores >= 0.7,]),symbol_lookup,by.x=0,by.y=1)
targetscan_list_70 = unique(targetscan_hits_70$affy_id)

targetscan_hits_60 = merge(as.matrix(targetscan[scores >= 0.6,]),symbol_lookup,by.x=0,by.y=1)
targetscan_list_60 = unique(targetscan_hits_60$affy_id)

targetscan_hits_50 = merge(as.matrix(targetscan[scores >= 0.5,]),symbol_lookup,by.x=0,by.y=1)
targetscan_list_50 = unique(targetscan_hits_50$affy_id)

targetscan_hits_40 = merge(as.matrix(targetscan[scores >= 0.4,]),symbol_lookup,by.x=0,by.y=1)
targetscan_list_40 = unique(targetscan_hits_40$affy_id)

targetscan_hits_30 = merge(as.matrix(targetscan[scores >= 0.3,]),symbol_lookup,by.x=0,by.y=1)
targetscan_list_30 = unique(targetscan_hits_30$affy_id)

targetscan_hits_20 = merge(as.matrix(targetscan[scores >= 0.2,]),symbol_lookup,by.x=0,by.y=1)
targetscan_list_20 = unique(targetscan_hits_20$affy_id)

targetscan_hits_10 = merge(as.matrix(targetscan[scores >= 0.1,]),symbol_lookup,by.x=0,by.y=1)
targetscan_list_10 = unique(targetscan_hits_10$affy_id)



```

## Gene Filtering
Use an Interquartile range calculation to filter invariant genes whose expression is largely static to reduce number of statistical tests for later.
```{r}
hist(apply(expression,1,IQR),breaks=50,main="Interquartile Range (IQR) Distribution",col=spectral)
print(paste(c("Size Before Filter: ",nrow(expression))))
filter <-  function(x) ( IQR(x) > 0.1 )
filtered = expression[genefilter(expression,filter),]
#filtered = filtered[genefilter(filtered,pOverA(p = 0.1, A = 3)),]
print(paste(c("Size After Filter:",nrow(filtered))))
```

## Statistical Analysis

### Setup of Stats
Build a simple contrast matrix, in this case HO vs WT.
```{r}
genotype <- as.factor(pdata$Genotype)
design <- cbind(model.matrix(~0+genotype))
colnames(design) = levels(genotype)
design

contrast.matrix <- makeContrasts("HO-WT", levels=design)
contrast.matrix
```


### Statistics - Linear Modeling
Use limma to fit an emperical bayes linear model to the contrast we are interested in.
```{r}

# Fit the linear model to either filtered or unfiltered data here
fit <- lmFit(filtered, design)
#fit <- lmFit(expression, design)

fit2 <- eBayes(contrasts.fit(fit, contrast.matrix))

# Transfer the Annotation Data to the fit2 object
fit2$genes$Symbol = genesymbols[as.character(rownames(fit2))]
fit2$genes$Description = genedescs[as.character(rownames(fit2))]
fit2$genes$Ensembl = gene_ens[as.character(rownames(fit2))]

sig_pval=0.01
sig_lfc=1

result <- decideTests(fit2, p.value=sig_pval, lfc=log2(sig_lfc), adjust="BH")
siglist=names(result[result[,1]!=0,])
stats=topTable(fit2,sort.by = "logFC",resort.by = "logFC",number=nrow(fit2))
stats_by_p=stats[order(stats$adj.P.Val),] 

up=sum(stats[siglist,]$logFC >= 0)
down=sum(stats[siglist,]$logFC <= 0)

```


## Post Statistical Quality control

### Volcano Plots
```{r}
plot(stats$logFC,-log10(stats$adj.P.Val),pch=19,cex=0.2,col="darkblue",main=paste("Volcanoplot Significance v Foldchange"),sub=paste("Up: ",up," genes, Down: ",down, "genes "),xlab="Log foldchange",ylab="-log10(Adj P-val)")
points(stats[siglist,]$logFC,-log10(stats[siglist,]$adj.P.Val),col="red")
points(stats[targetscan_list,]$logFC,-log10(stats[targetscan_list,]$adj.P.Val),col="green",pch=19,cex=0.2)
text(stats[rownames(stats_by_p)[1:20],]$logFC,-log10(stats[rownames(stats_by_p)[1:20],]$adj.P.Val),col="darkred",labels = stats[rownames(stats_by_p)[1:20],"ID.Symbol"],cex=0.5,pos=2)
abline(h=-log10(0.05),col="blue",lty=2)
abline(h=-log10(0.01),col="red",lty=2)
abline(v=log2(1.5),col="purple",lty=2)
abline(v=-log2(1.5),col="purple",lty=2)
legend("bottomleft",c("0.01 Sig","0.05 Sig"),lty=2,col=c("red","blue"),cex=0.4)
legend("bottomright",c("Log FC > 1"),lty=2,col=c("purple"),cex=0.4)
legend("topright","Up in HO\nrelative to WT",cex=0.4)
legend("topleft","Down in HO\nrelative to WT",cex=0.4)
legend("top",c("Sig.","TargetScan","all"),pch=c(19,19,19),col=c("red","green","darkblue"),cex=0.5)
```

### X/Y plots of significant hits
```{r}
wt_median=apply(expression[,pdata$Genotype=="WT"],1,median)
ko_median=apply(expression[,pdata$Genotype=="HO"],1,median)
plot(ko_median,wt_median,pch=19,cex=0.3,col="darkblue",main="Scatter WT vs HO")
points(ko_median[siglist],wt_median[siglist],col="red")
points(ko_median[targetscan_list],wt_median[targetscan_list],col="green",cex=0.3,pch=19)
text(ko_median[siglist],wt_median[siglist],col="red",labels = genesymbols[siglist],cex=0.4,pos=2)
legend("topright",c("Sig.","TargetScan","all"),pch=c(19,19,19),col=c("red","green","darkblue"),cex=0.5)
```

### MA Plots
```{r}
plot(wt_median+ko_median,wt_median/ko_median,cex=0.3,pch=19,col="darkblue",main="MA Plot WT vs HO")
points((wt_median+ko_median)[siglist],(wt_median/ko_median)[siglist],col="red")
points((wt_median+ko_median)[targetscan_list],(wt_median/ko_median)[targetscan_list],col="green",cex=0.3,pch=19)
abline(h=1,col="red",lty=2)
legend("topright",c("Sig.","TargetScan","all"),pch=c(19,19,19),col=c("red","green","darkblue"),cex=0.5)
```

### Heatmap of significant hits
```{r}
heatmap.2(expression[siglist,],trace="none",col=hmcol,cexRow=0.4,cexCol=0.4,labCol = pdata$Genotype,labRow = genesymbols[rownames(expression[siglist,])],main="All sig. hits")
heatmap.2(expression[rownames(stats_by_p[1:50,]),],trace="none",col=hmcol,cexRow=0.4,cexCol=0.4,labCol = pdata$Genotype,labRow = genesymbols[rownames(expression[rownames(stats_by_p[1:50,]),])],main="Top 50 sig. hits")
```

### Analysis of TargetScan mir29 genes in the expression set
```{r}
plot(ecdf(stats$logFC),pch=19,cex=0.1,col="darkblue",main="Expression S-curve (Bartel)",xlim=c(-2,2),xlab="ECDF Log Fold Change")
plot(ecdf(stats[targetscan_list,]$logFC),add=T,cex=0.1,pch=19,col="red")
abline(v=0,col="grey",lty=2)
legend("topleft",c("All genes","TargetScan miR-29"),col=c("darkblue","red"),lty=1,lwd=2,cex=0.4)

plot(ecdf(stats$logFC),pch=19,cex=0.1,col="darkblue",main="Expression S-curve (Bartel)",xlim=c(-2,2),xlab="ECDF Log Fold Change mir-29")
plot(ecdf(stats[targetscan_list,]$logFC),add=T,cex=0.1,pch=19,col="red")
plot(ecdf(stats[targetscan_list_90,]$logFC),add=T,cex=0.1,pch=19,col=spectral2[1])
plot(ecdf(stats[targetscan_list_80,]$logFC),add=T,cex=0.1,pch=19,col=spectral2[2])
plot(ecdf(stats[targetscan_list_70,]$logFC),add=T,cex=0.1,pch=19,col=spectral2[3])
plot(ecdf(stats[targetscan_list_60,]$logFC),add=T,cex=0.1,pch=19,col=spectral2[4])
plot(ecdf(stats[targetscan_list_50,]$logFC),add=T,cex=0.1,pch=19,col=spectral2[5])
plot(ecdf(stats[targetscan_list_40,]$logFC),add=T,cex=0.1,pch=19,col=spectral2[6])
plot(ecdf(stats[targetscan_list_30,]$logFC),add=T,cex=0.1,pch=19,col=spectral2[7])
plot(ecdf(stats[targetscan_list_20,]$logFC),add=T,cex=0.1,pch=19,col=spectral2[8])
plot(ecdf(stats[targetscan_list_10,]$logFC),add=T,cex=0.1,pch=19,col=spectral2[9])
abline(v=0,col="grey",lty=2)
legend("topleft",c("All genes","All TargetScan",paste("TargetScan Score > 0.",rev(seq(9:1)))),col=c("darkblue","red",spectral2),lty=1,lwd=2,cex=0.4)

```

### Median expression levels of TargetScan hits
```{r}
plot(wt_median,ko_median,pch=19,cex=0.1,main="Expression Skew, TargetScan",col="black")
points(wt_median[targetscan_list],ko_median[targetscan_list],pch=19,col="green",cex=0.1)
abline(lm(ko_median[targetscan_list] ~ wt_median[targetscan_list]),col="red")
abline(lm(ko_median ~ wt_median),col="purple")
legend("topleft",c("All genes","TargetScan miR-29"),lty=1,col=c("purple","red"),cex=0.4)
```

### Result Files TXT
```{r}
write.table(stats[!is.na(stats$ID.Ensembl),],"fold_change_affy_alena.txt",sep="\t",quote=F)
```


```{r}
targetscan=read.table("TargetScan7.1__miR-9-5p.predicted_targets.txt",row.names=1,sep="\t",header=T)

symbol_lookup=as.data.frame(genesymbols)
colnames(symbol_lookup)=c("affy_gene_name")
symbol_lookup$affy_id=rownames(symbol_lookup)

targetscan_hits=merge(as.matrix(targetscan),symbol_lookup,by.x=0,by.y=1)
targetscan_list = unique(targetscan_hits$affy_id)

scores=targetscan$Aggregate.PCT
scores=gsub("> ","",scores)
scores=gsub("< ","",scores)
scores=as.double(scores)



targetscan_hits_90 = merge(as.matrix(targetscan[scores >= 0.9,]),symbol_lookup,by.x=0,by.y=1)
targetscan_list_90 = unique(targetscan_hits_90$affy_id)

targetscan_hits_80 = merge(as.matrix(targetscan[scores >= 0.8,]),symbol_lookup,by.x=0,by.y=1)
targetscan_list_80 = unique(targetscan_hits_80$affy_id)

targetscan_hits_70 = merge(as.matrix(targetscan[scores >= 0.7,]),symbol_lookup,by.x=0,by.y=1)
targetscan_list_70 = unique(targetscan_hits_70$affy_id)

targetscan_hits_60 = merge(as.matrix(targetscan[scores >= 0.6,]),symbol_lookup,by.x=0,by.y=1)
targetscan_list_60 = unique(targetscan_hits_60$affy_id)

targetscan_hits_50 = merge(as.matrix(targetscan[scores >= 0.5,]),symbol_lookup,by.x=0,by.y=1)
targetscan_list_50 = unique(targetscan_hits_50$affy_id)

targetscan_hits_40 = merge(as.matrix(targetscan[scores >= 0.4,]),symbol_lookup,by.x=0,by.y=1)
targetscan_list_40 = unique(targetscan_hits_40$affy_id)

targetscan_hits_30 = merge(as.matrix(targetscan[scores >= 0.3,]),symbol_lookup,by.x=0,by.y=1)
targetscan_list_30 = unique(targetscan_hits_30$affy_id)

targetscan_hits_20 = merge(as.matrix(targetscan[scores >= 0.2,]),symbol_lookup,by.x=0,by.y=1)
targetscan_list_20 = unique(targetscan_hits_20$affy_id)

targetscan_hits_10 = merge(as.matrix(targetscan[scores >= 0.1,]),symbol_lookup,by.x=0,by.y=1)
targetscan_list_10 = unique(targetscan_hits_10$affy_id)

plot(ecdf(stats$logFC),pch=19,cex=0.1,col="darkblue",main="Expression S-curve (Bartel)",xlim=c(-2,2),xlab="ECDF Log Fold Change mir-9")
plot(ecdf(stats[targetscan_list,]$logFC),add=T,cex=0.1,pch=19,col="red")
plot(ecdf(stats[targetscan_list_90,]$logFC),add=T,cex=0.1,pch=19,col=spectral2[1])
plot(ecdf(stats[targetscan_list_80,]$logFC),add=T,cex=0.1,pch=19,col=spectral2[2])
plot(ecdf(stats[targetscan_list_70,]$logFC),add=T,cex=0.1,pch=19,col=spectral2[3])
plot(ecdf(stats[targetscan_list_60,]$logFC),add=T,cex=0.1,pch=19,col=spectral2[4])
plot(ecdf(stats[targetscan_list_50,]$logFC),add=T,cex=0.1,pch=19,col=spectral2[5])
plot(ecdf(stats[targetscan_list_40,]$logFC),add=T,cex=0.1,pch=19,col=spectral2[6])
plot(ecdf(stats[targetscan_list_30,]$logFC),add=T,cex=0.1,pch=19,col=spectral2[7])
plot(ecdf(stats[targetscan_list_20,]$logFC),add=T,cex=0.1,pch=19,col=spectral2[8])
plot(ecdf(stats[targetscan_list_10,]$logFC),add=T,cex=0.1,pch=19,col=spectral2[9])
abline(v=0,col="grey",lty=2)
legend("topleft",c("All genes","All TargetScan",paste("TargetScan Score > 0.",rev(seq(9:1)))),col=c("darkblue","red",spectral2),lty=1,lwd=2,cex=0.4)

```

```{r}
targetscan=read.table("TargetScan7.1__let-7-5p_miR-98-5p.predicted_targets.txt",row.names=1,sep="\t",header=T)

symbol_lookup=as.data.frame(genesymbols)
colnames(symbol_lookup)=c("affy_gene_name")
symbol_lookup$affy_id=rownames(symbol_lookup)

targetscan_hits=merge(as.matrix(targetscan),symbol_lookup,by.x=0,by.y=1)
targetscan_list = unique(targetscan_hits$affy_id)

scores=targetscan$Aggregate.PCT
scores=gsub("> ","",scores)
scores=gsub("< ","",scores)
scores=as.double(scores)



targetscan_hits_90 = merge(as.matrix(targetscan[scores >= 0.9,]),symbol_lookup,by.x=0,by.y=1)
targetscan_list_90 = unique(targetscan_hits_90$affy_id)

targetscan_hits_80 = merge(as.matrix(targetscan[scores >= 0.8,]),symbol_lookup,by.x=0,by.y=1)
targetscan_list_80 = unique(targetscan_hits_80$affy_id)

targetscan_hits_70 = merge(as.matrix(targetscan[scores >= 0.7,]),symbol_lookup,by.x=0,by.y=1)
targetscan_list_70 = unique(targetscan_hits_70$affy_id)

targetscan_hits_60 = merge(as.matrix(targetscan[scores >= 0.6,]),symbol_lookup,by.x=0,by.y=1)
targetscan_list_60 = unique(targetscan_hits_60$affy_id)

targetscan_hits_50 = merge(as.matrix(targetscan[scores >= 0.5,]),symbol_lookup,by.x=0,by.y=1)
targetscan_list_50 = unique(targetscan_hits_50$affy_id)

targetscan_hits_40 = merge(as.matrix(targetscan[scores >= 0.4,]),symbol_lookup,by.x=0,by.y=1)
targetscan_list_40 = unique(targetscan_hits_40$affy_id)

targetscan_hits_30 = merge(as.matrix(targetscan[scores >= 0.3,]),symbol_lookup,by.x=0,by.y=1)
targetscan_list_30 = unique(targetscan_hits_30$affy_id)

targetscan_hits_20 = merge(as.matrix(targetscan[scores >= 0.2,]),symbol_lookup,by.x=0,by.y=1)
targetscan_list_20 = unique(targetscan_hits_20$affy_id)

targetscan_hits_10 = merge(as.matrix(targetscan[scores >= 0.1,]),symbol_lookup,by.x=0,by.y=1)
targetscan_list_10 = unique(targetscan_hits_10$affy_id)

plot(ecdf(stats$logFC),pch=19,cex=0.1,col="darkblue",main="Expression S-curve (Bartel)",xlim=c(-2,2),xlab="ECDF Log Fold Change let-7")
plot(ecdf(stats[targetscan_list,]$logFC),add=T,cex=0.1,pch=19,col="red")
plot(ecdf(stats[targetscan_list_90,]$logFC),add=T,cex=0.1,pch=19,col=spectral2[1])
plot(ecdf(stats[targetscan_list_80,]$logFC),add=T,cex=0.1,pch=19,col=spectral2[2])
plot(ecdf(stats[targetscan_list_70,]$logFC),add=T,cex=0.1,pch=19,col=spectral2[3])
plot(ecdf(stats[targetscan_list_60,]$logFC),add=T,cex=0.1,pch=19,col=spectral2[4])
plot(ecdf(stats[targetscan_list_50,]$logFC),add=T,cex=0.1,pch=19,col=spectral2[5])
plot(ecdf(stats[targetscan_list_40,]$logFC),add=T,cex=0.1,pch=19,col=spectral2[6])
plot(ecdf(stats[targetscan_list_30,]$logFC),add=T,cex=0.1,pch=19,col=spectral2[7])
plot(ecdf(stats[targetscan_list_20,]$logFC),add=T,cex=0.1,pch=19,col=spectral2[8])
plot(ecdf(stats[targetscan_list_10,]$logFC),add=T,cex=0.1,pch=19,col=spectral2[9])
abline(v=0,col="grey",lty=2)
legend("topleft",c("All genes","All TargetScan",paste("TargetScan Score > 0.",rev(seq(9:1)))),col=c("darkblue","red",spectral2),lty=1,lwd=2,cex=0.4)

```

